supplmental

### 2020-01-01 paper_stats.Rmd
tables

  library(sjPlot)
  library(tidyverse)
  library(broom)
  library(knitr)
  library(xtable)

@@

  data_frame(Variable       = name.1(descript),
             N              = n.miss(descript),
             "Mean SD"      = summary.1(descript),
             "Median [IQR]" = med.iqr(descript),
             "(Min, Max)"   = min.max(descript)) %>%
  xtable()

@@

  full_join(means_df, difs_df, by = "Outcome") %>%
    select(Outcome, everything()) %>%
    kable()

@@

  vrs_df <- do.call(bind_rows, pmap(df, var_ratio))

  kable(vrs_df)

>>>>

  library(sjPlot)
  library(tidyverse)
  library(broom)
  library(knitr)
  library(flextable)

@@

  data_frame(Variable       = name.1(descript),
             N              = n.miss(descript),
             "Mean SD"      = summary.1(descript),
             "Median [IQR]" = med.iqr(descript),
             "(Min, Max)"   = min.max(descript)) %>%
  flextable()

@@

  full_join(means_df, difs_df, by = "Outcome") %>%
    select(Outcome, everything()) %>%
    flextable()

@@

  do.call(bind_rows, pmap(df, var_ratio)) %>%
    flextable()
